Case Study: Gene Set Enrichment Analysis (Mouse Data Set)

### 2018-07-12 datasets/GSEA/gsea-human.Rmd
Expand y-axis on pval histograms

```{r assumptions, message=FALSE, fig.width=10, fig.height=3.2}
## filter numInCat below only used for plotting
## filter numDEInCat for cases where there are no DE genes in the category (these are actually not tested)
#dplyr::filter( goRes, over_represented_pvalue == 1, numDEInCat > 0)
dplyr::filter( goRes, numDEInCat > 0, numInCat > 10 ) %>%
    strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=10)
```

>>>>

```{r assumptions, message=FALSE, fig.width=10, fig.height=3.2}
## filter numInCat below only used for plotting
## filter numDEInCat for cases where there are no DE genes in the category (these are actually not tested)
#dplyr::filter( goRes, over_represented_pvalue == 1, numDEInCat > 0)
dplyr::filter( goRes, numDEInCat > 0, numInCat > 10 ) %>%
    strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=18)
```

### 2018-07-12 datasets/GSEA/gsea-mouse.Rmd
Expand y-axis on pval histograms

```{r assumptions, message=FALSE, fig.width=10, fig.height=3.2}
## filter numInCat below only used for plotting
## filter numDEInCat for cases where there are no DE genes in the category (these are actually not tested)
#dplyr::filter( goRes, over_represented_pvalue == 1, numDEInCat > 0)
dplyr::filter(goRes, numDEInCat > 0, numInCat > 10) %>%
    strat_hist(pval = "over_represented_pvalue", covariate = "numInCat", maxy=10)
```

>>>>

```{r assumptions, message=FALSE, fig.width=10, fig.height=3.2}
## filter numInCat below only used for plotting
## filter numDEInCat for cases where there are no DE genes in the category (these are actually not tested)
#dplyr::filter( goRes, over_represented_pvalue == 1, numDEInCat > 0)
dplyr::filter(goRes, numDEInCat > 0, numInCat > 10) %>%
    strat_hist(pval = "over_represented_pvalue", covariate = "numInCat", maxy=35)
```
